Implementing simplified INLA into `aghq`

### 2022-10-11 src/dev_sinla/sinla.Rmd
Fixing missing minus sign in 2 * pi, and a header at wrong level

The Gaussian approximation $p_\text{G}(x \, | \, \theta, y)$ is previously used in computing the Laplace approximation to $p(\theta \, | \, y)$
$$
\begin{equation}
\tilde p(\theta \, | \, y) \propto \frac{p(x, \theta, y)}{p_\text{G}(x \, | \, \theta, y)} \Big\rvert_{x = \hat{\mu}(\theta)} = \frac{p(y, \hat{\mu}(\theta), \theta)}{\det(2 \pi \hat{Q}(\theta))^{1/2}}, (\#eq:pthetagiveny)
\end{equation}
$$
such that one easy way to calculate it is to use set `random = "x"` in the `TMB` template to integrate the latent field out, then recover the Gaussian approximation from there, as we have done in the function `h` above.
Let's optimise `h`:

@@

```{r}
denom <- 0.5 * log(det(2 * pi * Q))
denom
```

On the negative log-likelihood scale, the number we get is:

```{r}
-1 * (numer - denom)
```

@@

```{r}
h$fn(input_param[c("beta_prev", "log_sigma_phi_prev")])
```

@@

Another approach we might take is to calculate the full Laplace approximation
$$
\begin{align*}
  \tilde p(x_i \, | \, \theta, y) &\propto \frac{p(x, \theta, y)}{p_\text{G}(x_{-i} \, | \, x_i, \theta, y)} \Big\rvert_{x_{-i} = \hat{\mu}_{-i}(x_i, \theta)} \\
  &= \frac{p(y, x_i, \hat{\mu}_{-i}(x_i, \theta), \theta)}{\det(2 \pi \hat{Q}_{-i}(x_i, \theta))^{1/2}}
\end{align*}
$$
This is not practical in some settings as it involves recomputing the Gaussian approximation $p_\text{G}(x_{-i} \, | \, x_i, \theta, y)$ for each value of $(x_i, \theta)$ which can be too computationally expensive.
With of a bit of effort, we can implement this in `TMB` by passing in data where elements $i$ and $-i$ of the latent field are named as such (see Appendix for template).

@@

# Reproducing output from `obj`

@@

```{r}
denom <- 0.5 * log(det(2 * pi * Q))
denom
```

```{r}
-1 * (numer - denom)
```

@@

```{r}
obj$fn(transformed_param)
```

>>>>

The Gaussian approximation $p_\text{G}(x \, | \, \theta, y)$ is previously used in computing the Laplace approximation to $p(\theta \, | \, y)$
$$
\begin{equation}
\tilde p(\theta \, | \, y) \propto \frac{p(x, \theta, y)}{p_\text{G}(x \, | \, \theta, y)} \Big\rvert_{x = \hat{\mu}(\theta)} = \frac{p(y, \hat{\mu}(\theta), \theta)}{\det \left(\frac{1}{2 \pi} \hat{Q}(\theta) \right)^{1/2}}, (\#eq:pthetagiveny)
\end{equation}
$$
such that one easy way to calculate it is to use set `random = "x"` in the `TMB` template to integrate the latent field out, then recover the Gaussian approximation from there, as we have done in the function `h` above.
Let's optimise `h`:

@@

```{r}
denom <- 0.5 * (determinant(Q, logarithm = TRUE)$modulus - (nrow(Q) * log(2 * pi)))
denom
```

Note that we use `determinant` on the log-scale as it is more numerically stable than e.g. `log(det(...))`.
On the log-likelihood scale, the number we get is:

```{r}
numer - denom
```

@@

```{r}
-1 * h$fn(input_param[c("beta_prev", "log_sigma_phi_prev")])
```

@@

Another approach we might take is to calculate the full Laplace approximation
$$
\begin{align*}
  \tilde p(x_i \, | \, \theta, y) &\propto \frac{p(x, \theta, y)}{p_\text{G}(x_{-i} \, | \, x_i, \theta, y)} \Big\rvert_{x_{-i} = \hat{\mu}_{-i}(x_i, \theta)} \\
  &= \frac{p(y, x_i, \hat{\mu}_{-i}(x_i, \theta), \theta)}{\det(\frac{1}{2 \pi} \hat{Q}_{-i}(x_i, \theta))^{1/2}}
\end{align*}
$$
This is not practical in some settings as it involves recomputing the Gaussian approximation $p_\text{G}(x_{-i} \, | \, x_i, \theta, y)$ for each value of $(x_i, \theta)$ which can be too computationally expensive.
With of a bit of effort, we can implement this in `TMB` by passing in data where elements $i$ and $-i$ of the latent field are named as such (see Appendix for template).

@@

## Reproducing output from `obj`

@@

```{r}
denom <- 0.5 * (determinant(Q, logarithm = TRUE)$modulus - (nrow(Q) * log(2 * pi)))
denom
```

```{r}
numer - denom
```

@@

```{r}
-1 * obj$fn(transformed_param)
```
